### 2015-02-06 cav-2015-tex/bisimulation.tex
Added introductory paragraph to the proof section

\section{Bisimilarity Proof}
\label{sec:bisim}
The theoretical result is the existence of a bisimulation between sets of states
states related by GSE ($p \rgse p^\prime$)
and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the
properties in \secref{sec:sh} with the constraint that
the states are \emph{feasible}: successors exist unless at
\cfgt{end}. Let $p \rgse p^\prime$ be a union over relations for GSE (see appendix):
$\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access after evaluating the expression for
the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
\cfgnt{k}\rp$, \emph{W} is a field write after evaluating the
expression for the right operand $\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in GSE: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.

>>>>

\section{Bisimilarity Proof}
\label{sec:bisim}
This section establishes the correctness of the~\symtxt{}. Demonstrating correctness is important because many summary heap techniques are correct only when certain, often unstated, assumptions are made. To show the absence of such assumptions, it is necessary to demonstrate soundness and completess with respect to all properties provable by symbolic execution. The proof relies on the observation that a state in symbolic execution can be thought of as representing a set of possible concrete states. Similarly, a state in the~\symtxt{} machine represents a set of possible~\gsetxt{} states. The goal is to show that states in the~\symtxt{} machine behave exactly like the sets of~\gsetxt{} states that they represent.

The main theoretical result establishes the existence of a bisimulation between sets of states
states related by GSE ($p \rgse p^\prime$)
and states related by the algorithm in this paper ($q \rsym q^\prime$). The relations are on the universe of \emph{well-formed} states $S$, which have the
properties in \secref{sec:sh} with the constraint that
the states are \emph{feasible}: successors exist unless at
\cfgt{end}. Let $p \rgse p^\prime$ be a union over relations for GSE (see appendix):
$\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rcom$, where \emph{A} is a field access after evaluating the expression for
the base reference $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
\cfgnt{k}\rp$, \emph{W} is a field write after evaluating the
expression for the right operand $\lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare after evaluating the
left and right operands $\lp \cfgnt{v}\ \cfgt{=}\ \cfgnt{*}
\rightarrow \cfgnt{k}\rp$, the prime symbol indicates a null reference
in the operation or a false outcome, and \emph{\com} is everything
else in the language. Any state relation, say $\rightarrow_x$, is
trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of
states. From this extension, a new meta transition relation is defined
over sets of states as
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\com
$$
The relation captures the notion of splitting groups of heaps at
certain operations. For example, suppose we have a set $P$ containing a single state $p$
with all references uninitialized. If $p$ is a field access state, it has two
potential successors in GSE: a non-null reference and a null reference. 
Thus, the $\rsgse$ relation has two successors and divides $P$ into the two outcomes.
